\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-01-31 doc/publications/plos16/plos16.tex
Reword a sentence in part 2

We therefore investigate the highest-ranked features not amongst the associated gene list by Duncan {\it et al.}~\cite{Duncan.2011}. 
%DENIS is this correct about the transcription factor binding site?
COLEC10 (collectin 10) contains variants more recently associated with BDM~\cite{Kemp2014,Liu2008}, with a transcription factor binding site for the known BMD gene FOXL1 overlapping the highly ranked variant.
%However, we also observe that from the set of highest-ranked features, for example, the top ten, not all of them exist
%within close proximity to known BMD genes. We investigate the literature to determine the plausibility of these variants
%contributing to BMD.
%One gene is COLEC10 (collectin 10). Featuring a transcription factor binding site for FOXL1, COLEC10 is also reported as
%containing variants associated with BMD \cite{Kemp2014,Liu2008}. However there currently exists no information on how this gene
%may contribute to BMD. 
Also highly-ranked are variants in chromosome 22q11. Stagi {\it et al.}~\cite{Stagi.2010}, observe that individuals with a
microdeletion in this region have a significant reduction in bone mass. In this same region, we also observe
variants present in PRODH (proline dehydrogenase). PRODH catalyzes the first step in proline degradation, and as
proposed by Phang {\it et al.}~\cite{Phang.2008}, proline is made available by collagen degradation.

>>>>

We therefore investigate the highest-ranked features not amongst the associated gene list by Duncan {\it et al.}~\cite{Duncan.2011}. 
%DENIS is this correct about the transcription factor binding site?
COLEC10 (collectin 10) contains variants more recently associated with BDM~\cite{Kemp2014,Liu2008}, with a verified transcription factor binding site for the known BMD gene FOXL1.
%However, we also observe that from the set of highest-ranked features, for example, the top ten, not all of them exist
%within close proximity to known BMD genes. We investigate the literature to determine the plausibility of these variants
%contributing to BMD.
%One gene is COLEC10 (collectin 10). Featuring a transcription factor binding site for FOXL1, COLEC10 is also reported as
%containing variants associated with BMD \cite{Kemp2014,Liu2008}. However there currently exists no information on how this gene
%may contribute to BMD. 
Also highly-ranked are variants in chromosome 22q11. Stagi {\it et al.}~\cite{Stagi.2010}, observe that individuals with a
microdeletion in this region have a significant reduction in bone mass. In this same region, we also observe
variants present in PRODH (proline dehydrogenase). PRODH catalyzes the first step in proline degradation, and as
proposed by Phang {\it et al.}~\cite{Phang.2008}, proline is made available by collagen degradation.
